Contracts for unions and intersections are hard for Nickel

### 2021-04-27 paper.tex
Add short section on performance/parallelization

>>>>

\subsection{Performance considerations}
\info{This a draft}
\todo{transition, location}

At first sight, performance should not be a critical issue given the use cases
of Nickel. But generating large configurations can already hit some limits in
current related languages [reference?]. A natural is parallelization:
Nickel being an almost pure functional programming language, evaluating separate
files or expressions in parallel is straightforward and effective. This
parallelization potential is thus a design requirement, and must be when the
addition of union types.
